Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning

### 2018-08-28 paper/paper.tex
updated paper

\usepackage{graphicx}
%\usepackage{nicefrac}

@@

%%%%%%%%%%%%%
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Motion Execution
% 
\title{Distributed Real-time Trajectory Replanning for Robust Motion Execution}% in Multi-Robot Systems}

%
%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
We propose a method for robust motion execution that can be applied to a wide range  of  trajectory execution tasks. 
It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
However, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.

We propose a method for robust motion execution that can be applied to wide range of trajectory execution tasks. It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or other external disturbances.
Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense their neighbors' positions and the obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory (b).
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
Our method relies on the \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.

We show in simulations that our method avoids collisions and deadlocks more successfully compared to ORCA~\cite{orca}.
Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.

@@

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
The general problem we would like to solve can be formulated as follows. 
Consider a group of $m$ robots. Each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i\th$ robot where time } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ order of derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R(\vp)&:\text{ collision model of a robot at position $\vp$ (sphere with radius $r_s$), and}\\
    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
\end{align*}

Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of its neighbors as well as the current occupied space $\cO_i$ around it.
We represent $\cO_i$ as a set of $\uptheta$ convex obstacles; our approach can accommodate for different sensing modalities, including LIDAR and RGB-D cameras.
%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ must execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We solve this problem approximately, using a dynamic receding horizon approach iteratively.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

This section introduces important mathematical concepts and notation that will be used throughout the paper.

\subsection{Buffered Voronoi Cell} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_s \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_s\leq 0 \right\}, \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of the vector $\vp$.

@@

% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
% \begin{align}
%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
% \end{align}

Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.

@@

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j\th$ piece where $j \in \{1,2,\ldots,l\}$. $\vf^{K}_{i,j}(t)$ denotes the $j\th$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$. $\vP^{K}_{i,j,\rho}$ denotes the $\rho\th$ control point of the $j\th$ piece where $\rho \in \{0,1,\ldots,d\}$.

@@

A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
Notice that all constraints should be linear in the decision variables.

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative. This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane. If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points. All 3 types of constraints are linear in control points. The construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$.
In each iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.

@@

%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
%We use this discrete path as an initial guess in trajectory optimization.
%If discrete planning is not required, we use the control points of the previous plan as the initial guess.

%We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
%In both cases, buffered Voronoi cells are used to ensure collision-free operation for up to time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.

%Dynamic limits cannot be represented as linear constraints in our QP.
%Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
%As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving of the QP.

At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c\th$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration. We execute this trajectory for a period of $\delta t$ and replan for the next iteration.

\begin{figure}
\centering
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{0.9\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {Discrete replanning required?};
    \node (discretesearch) [process, right of=discrete, xshift=1.5cm, yshift = 1cm, text width = 2cm] {Discrete Search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {Construct QP};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {Construct QP};
    %\node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    %{constraint builder};
    \node (trajopt) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width = 2.5cm] {Trajectory Optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 2.0cm, text width = 2cm] {Dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {Rescaling};
    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

@@

    \draw [arrow] (discrete) -- node[anchor=south] {Yes} (discretesearch);
    \draw [arrow] (discrete) -- node[anchor=north] {No} (contobjbuild);
    \draw [arrow] (discretesearch) -- (discobjbuild);
    \draw [arrow] (discobjbuild) -- (trajopt);
    \draw [arrow] (contobjbuild) -- (trajopt);
    %\draw [arrow] (constraintbuild) -- (trajopt);
    \draw [arrow] (trajopt) -- (dynamiclimits);
    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Start next iteration} -|   (discrete);
    \draw [arrow] (dynamiclimits) -- node[anchor=east] {Yes} (rescale);
    \draw [arrow] (rescale) -| (trajopt);

@@

\subsection{Theoretical Guarantees} %maybe

>>>>

\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage{nicefrac}

@@

%%%%%%%%%%%%%
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}
\newcommand{\changed}[1]{\textcolor{purple}{#1}}

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Trajectory Execution
% 
\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}% in Multi-Robot Systems}

% Distributed Real-time Trajectory Replanning for Robust Trajectory Execution
% Robust Trajectory Execution for Distributed Multi-Robot Systems
% Robust Trajectory Execution for Distributed UGV Teams
% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Planning
% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Replanning
% Robust Trajectory Execution for Distributed Multi-Robot Teams Using Real-time Replanning

%
\titlerunning{Robust Trajectory Execution for Multi-Robot Teams}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
Robust trajectory execution is an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
We propose an algorithm for robust trajectory execution that compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, imperfect motion execution, and external disturbances.
Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
At the low-level, we use buffered Voronoi cells as a multi-robot collision avoidance strategy.
Compared to ORCA, our approach supports higher-order dynamic limits and avoids deadlocks better.
We demonstrate our approach in simulation and on physical robots, showing that it can operate in real time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is particularly important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives such as total energy used~\cite{crazyplanning-ieeetro};
however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.

To compensate for changes in the environment or imperfect execution, one might apply cooperative collision avoidance strategies, such as ORCA~\cite{orca}, at runtime.
However, such algorithms often operate locally and do not take the pre-planned trajectories into account.
Robust trajectory execution, on the other hand, avoids future collision more effectively because it directly considers pre-planned trajectories.
Consider the example in Fig.~\ref{fig:swap2}(a), where two robots must swap positions.
The pre-planned trajectories are collision-free, but they do not consider the newly introduced obstacle and the blue robot does not start at its correct location.
However, the pre-planned trajectories can be used as guidance for replanning.
In this example, robots can get stuck if a local cooperative collision avoidance strategy is applied.
%We propose robust trajectory execution as an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
%Our algorithm compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
%Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
%Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
Using our method, the robots can successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense other robots' positions and the obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{(a) Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines).
The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
(b) Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory.
}
\label{fig:swap2}
\end{figure}

Robust trajectory execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
Our method relies on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.
%We also apply our dynamic receding horizon approach to ORCA and show that it helps to avoid deadlocks more effectively in that case, although the ORCA-based solution does not support higher-order dynamic limits.

% The contributions of this work are
The main contribution of this work is a novel distributed algorithm for robust trajectory execution that considers higher-order dynamic limits.
It also compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
%It also compensates for environmental changes and imperfect trajectory execution.
We show in simulations that our method avoids deadlocks better than ORCA~\cite{orca}.
Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.

@@

% Our method is closely related to cooperative collision avoidance.
% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
Safety barrier certificates achieve collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
Our robust trajectory execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)

While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
%Polynomial trajectories can be generated using a QP~\cite{richterISRR} without taking obstacles directly into account.
%QP-based formulations on B-splines or B\'ezier curves have been used to consider obstacles in form of linear hard constraints~\cite{flores,tang}.
%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
The optimization can use a discrete plan as an initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
The general problem we would like to solve can be formulated as follows. 
Consider a group of $m$ robots. Each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory $(\R\to \R^n)$ of $i\th$ robot where time } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ order of derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\ %(we use a sphere with }
     %     & \text{radius $r_s$, but $R(\vp)$ can be any convex shape), and}\\
    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
\end{align*}

Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of other robots as well as the current occupied space $\cO_i$ around it\footnote{Since our approach can accommodate many sensing modalities, we do not provide a specific sensing capability in the general problem.}.
We represent $\cO_i$ as a set of $\uptheta$ convex obstacles.
%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ must execute a trajectory $\vf_i(t)$, where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision-free, and}\\ 
    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We solve this problem approximately, using a dynamic receding horizon approach iteratively.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to the user-provided period $\delta t$.
We set $R(\vp)$ to a sphere with radius $r_s$ centered at $\vp$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

This section introduces important mathematical concepts and notations that will be used throughout the paper.

\subsection{Buffered Voronoi Cell} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_s \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_s\leq 0 \right\}, \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L$^{2}$-norm of the vector $\vp$.

@@

% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
% \begin{align}
%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
% \end{align}
Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.

@@

We use splines as trajectories with user-specified number of pieces ($l$) and degree ($d$), where each piece is a degree $d$ B\'ezier curve.
Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j\th$ piece where $j \in \{1,2,\ldots,l\}$.
$\vf^{K}_{i,j}(t)$ denotes the $j\th$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$. $\vP^{K}_{i,j,\rho}$ denotes the $\rho\th$ control point of the $j\th$ piece where $\rho \in \{0,1,\ldots,d\}$.

@@

A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. 
The quadratic cost function we use is described in Section~\ref{continuousOptimization}.

The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
Notice that all constraints should be linear in the decision variables.
There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector in a specified degree of differentiation. This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane. If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points. All three types of constraints are linear in control points. The exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$.
In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory \changed{$\vf^K_i(t)$}.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.

@@

In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
If discrete planning is required, we execute a discrete search that results in a discrete path that is collision-free but not smooth.
We use this discrete path as an initial guess in trajectory optimization.
If discrete planning is not required, we use the control points of the previous plan as the initial guess.

We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
In both cases, buffered Voronoi cells are used to ensure collision-free operation for time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.

Dynamic limits cannot be represented as linear constraints in our QP.
Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
While dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, and since the initial point constraints are violated when the durations are increased, we re-solve the QP.

At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$; is continuous up to the $c\th$ derivative; obeys the dynamic limits of the robot; tries to stay close to the original trajectory; and is a good starting point for the next iteration. We execute this trajectory for a period of $\delta t$ and replan for the next iteration.

\begin{figure}
\centering
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{1.0\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {Discrete replanning required?};
    \node (discretesearch) [process, right of=discrete, xshift=1.5cm, yshift = 1cm, text width = 2cm] {Discrete Search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {Construct QP};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {Construct QP};
    %\node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    %{constraint builder};
    \node (trajopt) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width = 2.5cm] {Trajectory Optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 2.0cm, text width = 2cm] {Dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {Rescaling};
    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

@@

    \draw [arrow] (discrete) -- node[anchor=south] {Yes} (discretesearch);
    \draw [arrow] (discrete) -- node[anchor=north] {No} (contobjbuild);
    \draw [arrow] (discretesearch) -- (discobjbuild);
    \draw [arrow] (discobjbuild) -- (trajopt);
    \draw [arrow] (contobjbuild) -- (trajopt);
    %\draw [arrow] (constraintbuild) -- (trajopt);
    \draw [arrow] (trajopt) -- (dynamiclimits);
    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Execute for $\delta t$ and start next iteration} -|   (discrete);
    \draw [arrow] (dynamiclimits) -- node[anchor=east] {Yes} (rescale);
    \draw [arrow] (rescale) -| (trajopt);

@@

\subsection{Theoretical Guarantees} \label{theoreticalGuarantees}
